### 2022-09-26 README.Rmd
name changed!

# nhanesTrends <img src="man/figures/logo.png" align="right" height="139" />

@@

``` r
# install.packages("remotes")
remotes::install_github("jhs-hwg/nhanesShinyBP")
```

@@

library(nhanesShinyBP)
app_run()

>>>>

# cardioStats.USA <img src="man/figures/logo.png" align="right" height="139" />

@@

``` r
# install.packages("remotes")
remotes::install_github("jhs-hwg/cardioStats.USA")
```

@@

library(cardioStats.USA)
app_run()
